Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-09-24 nir_companions.tex
Average -> medain amplitude in caption.

    \subsection{Relative differential amplitude}
    To probe this issue further we investigated how the amplitude of the differential signal changed with \(\Delta RV\). Taking the same PHOENIX-ACES spectra (\(T_{\textrm{eff}} = 2500~K\), \(\rm logg=5.0\), \(\rm [Fe/H]=0.0\)), we computed differential spectra for a range of \(\Delta RV\)s between \(\pm10\)\kmps{}. Figure~\ref{fig:diff_amp} shows how the relative amplitude of the differential spectrum in the wavelength range 2110--2123~nm (detector 1 of our CRIRES observations) changed as the spectra are offset. At each RV step we take the maximum absolute differential value found. These are then normalized by the median value outside of the line FWHM (dashed vertical lines), between \(\pm(7-10)\)\kmps{}, to give a relative differential amplitude, independent from the depth of a specific line. For comparison we also show the relative amplitude of the differential spectrum for a single Gaussian and Lorentzian line when Doppler shifted by the same \(\Delta RV\)s. The shape of these results is also consistent with the analytical form of the differential spectra~\citet[][eqn.~A.1]{ferluga_separating_1997}.

@@

    \begin{figure}
        \centering
        \includegraphics[width=0.8\hsize]{images/fig12.pdf}
        \caption{Simulated relative amplitude of differential spectra at different RV separations revealing the diminished amplitude at small orbital separations. The solid blue line shows the maximum relative amplitude of the differential signal (from a shifted copy of itself) of a PHOENIX-ACES spectrum with \(T_{\textrm{eff}}=2500~K, \textrm{logg}=5.0, \textrm{[Fe/H]}=0.0\), in the wavelength region 2110--2123~nm. The maximum difference is normalized by the average amplitude between 7--10\kmps{}, representing a complete line separation. The orange (dashed) and green (dot-dashed) lines represent the relative amplitude of a differential spectrum for a single Gaussian and single Lorentzian absorption line respectively, each with a unitary amplitude and a \(\rm FWHM = \lambda / R\). \textbf{\st{ Beyond the FWHM lines the difference of the synthetic spectrum becomes more complicated due to the interaction of neighbouring lines.}} The solid vertical lines indicate the estimated companion \(\Delta RV\) in these observations while the dashed vertical lines indicate the RV corresponding to the FWHM at this wavelength and resolution. Beyond the FWHM RV the synthetic spectrum becomes complicated due to the interaction of neighbouring lines.}

>>>>

    \subsection{Relative differential amplitude}
    To probe this issue further we investigated how the amplitude of the differential signal changed with \(\Delta RV\). Taking the same PHOENIX-ACES spectra (\(T_{\textrm{eff}} = 2500~K\), \(\rm logg=5.0\), \(\rm [Fe/H]=0.0\)), we computed differential spectra for a range of \(\Delta RV\)s between \(\pm10\)\kmps{}. Figure~\ref{fig:diff_amp} shows how the relative amplitude of the differential spectrum in the wavelength range 2110--2123~nm (detector 1 of our CRIRES observations) changed as the spectra are offset. At each RV step we take the maximum absolute differential value found. These are then normalized by the median value outside of the line FWHM (dashed vertical lines), between \(\pm(7\)--10\kmps{}, to give a relative differential amplitude, independent from the depth of a specific line. For comparison we also show the relative amplitude of the differential spectrum for a single Gaussian and Lorentzian line when Doppler shifted by the same \(\Delta RV\)s. The shape of these results is also consistent with the analytical form of the differential spectra~\citet[][eqn.~A.1]{ferluga_separating_1997}.

@@

    \begin{figure}
        \centering
        \includegraphics[width=0.8\hsize]{images/fig12.pdf}
        \caption{Simulated relative amplitude of differential spectra at different RV separations revealing the diminished amplitude at small orbital separations. The solid blue line shows the maximum relative amplitude of the differential signal (from a shifted copy of itself) of a PHOENIX-ACES spectrum with \(T_{\textrm{eff}}=2500~K, \textrm{logg}=5.0, \textrm{[Fe/H]}=0.0\), in the wavelength region 2110--2123~nm. The maximum difference is normalized by the median amplitude between \(\pm7\)--10\kmps{}, representing a complete line separation. The orange (dashed) and green (dot-dashed) lines represent the relative amplitude of a differential spectrum for a single Gaussian and single Lorentzian absorption line respectively, each with a unitary amplitude and a \(\rm FWHM = \lambda / R\). \textbf{\st{ Beyond the FWHM lines the difference of the synthetic spectrum becomes more complicated due to the interaction of neighbouring lines.}} The solid vertical lines indicate the estimated companion \(\Delta RV\) in these observations while the dashed vertical lines indicate the RV corresponding to the FWHM at this wavelength and resolution. Beyond the FWHM RV the synthetic spectrum becomes complicated due to the interaction of neighbouring lines.}
